---
title: "Replication of 'The Relationship Between Mental Representations of Welfare Recipients and Attitudes Toward Welfare' by Brown-Iannuzzi, J. L., Dotsch, R., Cooley, E., & Payne, B. K. (2016, Psychological Science)"
author: "Catherine Thomas (ccthomas@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---

# Introduction

<!-- [No abstract is needed.]  Each replication project will have a straightforward, no frills report of the study and results.  These reports will be publicly available as supplementary material for the aggregate report(s) of the project as a whole.  Also, to maximize project integrity, the intro and methods will be written and critiqued in advance of data collection.  Introductions can be just 1-2 paragraphs clarifying the main idea of the original study, the target finding for replication, and any other essential information.  It will NOT have a literature review -- that is in the original publication. You can write both the introduction and the methods in past tense.   -->

Brown-Iannuzzi et al. (2016) investigate the extent to which opposition to welfare may be driven by negative stereotypes, or mental representations, of welfare recipients. In Study 1, images of stereotypic welfare and non-welfare faces were generated through a reverse correlation task in which participants selected the image in a pair of faces that looked more like a welfare recipient. In Study 2, a separate sample was shown these images of interest (the welfare and non-welfare faces) and asked to rate these images on various characteristics, such as race, laziness, responsibility, competence, autonomy. As predicted, the stereotypic welfare recipient image generated from Study 1 was rated in Study 2 in line with stereotypes of welfare recipients and African Americans. Study 3 sought to examine how these stereotypes influenced support for welfare and found that participants were less likely to rate the welfare images as responsible and less likely to support giving them welfare compared to the stereotypic non-welfare face.

In this project, we replicated the Study 3 replication with Study 1 images as presented in the supplemental materials. The original study found that participants were much more likely to rate the stereotypic welfare image as less intelligent, hardworking, less reponsible broadly, and less responsible with both food stamps and cash assistance. They found support for their primary hypothesis that participants were less likely to support giving the person in the welfare image food stamps or cash assistance than the person in the non-welfare image. The primary test that this study seeks to replicate is the difference in support for cash assistance between the welfare and non-welfare images from Study 1.        

# Methods
A sample of 58 participants will be recruited from Amazon Mechanical Turk. Using a within-subjects design, participants will be told they will see a series of "fuzzy" images and will be asked to make judgments about the face in the images based on a glance. They are told that the images are composite photos of applicants to government assistance programs and that some of the people were responsible with the benefits while others were not. They are asked to rate each image on the extent to which the person appears intelligent, hardworking, responsible, responsible with use of food stamps, and responsible with use of cash assistance. They are also asked how supportive they would be to give this person food stamps or cash assistance. 

To review the experiment, click [here](https://stanforduniversity.qualtrics.com/SE/?SID=SV_cBlO9F37Q77ESAB).

## Power Analysis

<!-- Original effect size, power analysis for samples to achieve 80%, 90%, 95% power to detect that effect size.  Considerations of feasibility for selecting planned sample size. -->

The original study (n=234) found that participants were less supportive of giving cash assistance to the welfare-recipient image (M = 2.95, 95% CI [2.78, 3.13]) compared to the non-recipient image (M = 3.80, 95% CI [3.65, 3.96]), η^2^= 0.26. The original power to detect this effect, using a repeated measures ANOVA, was 0.99. This original study was a replication of Study 3 (n=229) in the primary paper which found that participants were less supportive of giving cash assistance to the welfare-recipient image (M = 3.57, 95% CI [3.40, 3.75]) compared to the non-recipient image (M = 4.19, 95% CI [4.03, 4.35]), η^2^=0.13. We use a weighted average of these η^2^ effect sizes (η^2^=0.20) to conduct the power analyses.

To achieve 80% power, the required sample size would be 35. 
To achieve 90% power, the required sample size would be 45.
To achieve 95% power, the required sample size would be 55.
To achieve 99% power, the required sample size would be 77.

## Planned Sample

The planned sample size is 58 with a target of 55 fully satisfying the eligibility criteria. There will be no termination rule. The exclusion rules will be failing to commit to carefully reading the content of the experiment, failing the instructional manipulation check a second time, selecting the same response option across all items, and having completed the study in under 6 minutes.  


## Materials & Procedure
All of the materials, including the images and scales, for this study were published freely online at [Mental Representations of Welfare Recipients](https://dx.doi.org/10.6084/m9.figshare.c.3468495.v2). 

The procedure described in the supplemental materials was followed, as follows:

> "Participants were told they would see a series of “fuzzy” images of real people. As an explanation for the blurry nature of the images, participants were told that the images look distorted because they were a composite of photos of people who have applied for government welfare programs. Additionally, participants were told some of the applicants turned out to be responsible recipients of welfare benefits, while others were irresponsible recipients of the benefits. Then, participants were asked to make a series of judgements about each image. Importantly, participants were given no indication whether the image was supposedly a composite of responsible or irresponsible welfare recipients. Participants then rated four filler images (the same filler images used in Study 1 and 2) so that the comparison between the two images of interest would not be salient to participants. The images of interest were the average welfare and non-recipient images generated from Study 1.
To replicate key findings from Study 1, participants first rated each image on the degree to which the pictured person seemed intelligent (1 = extremely unintelligent; 6 = extremely intelligent) and hardworking (1 = extremely lazy; 6 = extremely hardworking). Then, participants were asked the extent to which the pictured person seemed responsible (1 = extremely irresponsible; 6 = extremely responsible). We also asked participants the extent to which they believed the pictured person would use food stamps responsibly (1 = definitely would not use responsibly; 6 = definitely would use responsibly), and would use cash assistance responsibly (1 = definitely would not use responsibly; 6 = definitely would use responsibly). Finally, participants were asked how supportive they would be to give the pictured person food stamps (1 = completely unsupportive; 6 = completely supportive) and cash assistance (1 = completely unsupportive; 6 = completely supportive). The participants also completed demographic information including gender, age, and race/ethnicity."

# Analysis Plan

The means and 95% CIs for the ratings of the two images of interest (welfare and non-welfare as generated in Study 1) on support for cash assistance will be generated in addition to the η^2^ value from a repeated measures ANOVA. Any observations with missing data on the variables for the key analysis will be excluded. While not explicitly stated, it appears as though the original authors used this exclusion rule. No covariates will be used. 

<!-- **Clarify key analysis of interest here**  You can also pre-specify additional analyses you plan to do. -->

For the **key analysis of interest, the η^2^ effect size will be calculated on the difference between the ratings of support of cash assistance for the welfare image compared to the non-welfare image**. This η^2^ will take into account the within-subjects correlations between the two image ratings. The replication will be considered successful if the effect size is statistically greater than zero. 

As a supplmental analysis, we will run a paired t-test to assess whether ratings on support for cash assistance for the welfare image are statistically greater than those for the welfare image. This is because a paired t-test is more standard in the literature.

We will conduct additional analyses on support for universal basic income programs. After the replication is complete (i.e. the two images of interest and the four filler images have been shown in random order), we will conduct exploratory analyses to test the effects of different messaging around a proposed welfare program of universal basic income. Participants will be randomly assigned to one of two messages regarding a new government benefits program. One arm will present a typical "universal basic income"" program messaging, the second will present a "social security for all" messaging. Support for the policy will then be assessed. Participants will then be shown the two images of interest (in random order) and asked to assess perceived responsiblity of the applicant with basic income and their support of giving the applicant basic income. 

For this additional analysis, first, we will first conduct a t test to assess whether support for basic income is statistically different in the "social security for all" condition than in the "universal basic income" condition. Second, we will conduct a t-test to assess whether the difference in ratings of support for basic income between the welfare and non-welfare images is statistically different in the "universal basic income" arm than in the "social security for all" arm. 

## Differences from Original Study

<!-- Explicitly describe known differences in sample, setting, procedure, and analysis plan from original study.  The goal, of course, is to minimize those differences, but differences will inevitably occur. Also, note whether such differences are anticipated to make a difference based on claims in the original article or subsequent published research on the conditions for obtaining the effect. -->

The only known deviation from this procedure was with regards to the filler images and the instructional manipulation check. The filler images for the current study were selected at random from the 400 images used in Study 1 available from the online open source materials but may not have been the same filler images used in the original study. An instructional manipulation check was developed for the purposes of this study and likely differed from that used in the original study. The filler images selected may affect the outcomes as they are all visibly different in their photo quality from the welfare image photo in particular, which may make the welfare image seem particularly salient to participants.

<!-- ### Methods Addendum (Post Data Collection) -->

<!-- <!-- You can comment this section out prior to final report with data collection. --> -->

<!-- #### Actual Sample -->
<!--   Sample size, demographics, data exclusions based on rules spelled out in analysis plan. -->

<!-- #### Differences from pre-data collection methods plan -->
<!--     Any differences from what was described as the original plan, or “none”. -->


# Results


### Data preparation

Data preparation following the analysis plan.

#### Load Relevant Libraries and Functions
```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(foreign)
library(forcats)
library(car)
library(knitr)
library(heplots)
sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
ci95.norm <- function(x) {
  me <- sem(x) * qnorm(.975)
  c(mean(x) - me, mean(x) + me)
}
ci <- function(x) {sem(x) * 1.96}
```

#### Import data	
```{r loaddf}
d <- read_csv("../data/pilot_b_data.csv", na = c("", "NA")) 
``` 

#### Data exclusion / filtering and preparing for data analysis
```{r tidy}
tidy.d <- d %>%
  rename(ID = V1) %>%
  select(ID, Smart_W, Hardwork_W, Response_W, FoodR_W, FoodS_W, CashR_W,
  CashS_W, Smart_NW, Hardwork_NW, Response_NW, FoodR_NW, FoodS_NW, CashR_NW, 
  CashS_NW) %>%
  na.omit(cols=CashS_W, CashS_NW) %>%
  mutate_each(funs(as.numeric(., na.rm=TRUE)), contains("_W")) %>%
  mutate_each(funs(as.numeric(., na.rm=TRUE)), contains("_NW")) %>%
  gather(Smart_W, Hardwork_W, Response_W, FoodR_W, FoodS_W, CashR_W,
  CashS_W, Smart_NW, Hardwork_NW, Response_NW, FoodR_NW, FoodS_NW, CashR_NW, 
  CashS_NW, key=Question, value=rating) %>%
    separate(Question, c("Question", "Image"), "_") %>%
  mutate(Image = fct_recode(Image, "NonWelfare"="NW", "Welfare"="W"))

tidy.d$Question = as.factor(tidy.d$Question)
length(unique(tidy.d$ID))
```

### Confirmatory analysis

The analyses as specified in the analysis plan.  

**Means and 95% CIs: Ratings of Support for Cash Assistance**
```{r means}
# getting table of means and 95%CI for ratings of welfare and non-welfare images
ms <- tidy.d %>% 
  mutate(Question = fct_recode(Question, "Responsible"="Response", "Responsible w Cash Asst"="CashR", "Support of Cash Asst"="CashS", "Responsible w Food Stamps"="FoodR", "Support of Food Stamps"="FoodS", "Hardworking"="Hardwork")) %>%
  group_by(Question, Image) %>% # it removes the last var granularity 
  summarise(Mean_Rating = mean(rating, na.rm=TRUE), 
  sd = sd(rating), 
  sem = sem(rating), 
  "ci" = ci(rating), 
  ci.lo = Mean_Rating - ci, 
  ci.hi = Mean_Rating + ci)
```

**ANOVA: Ratings of Support for Cash Assistance**
```{r etasq}
# η^2^ effect size of diff btw welfare and non-welfare images on support for cash assistance
df <- tidy.d[tidy.d$Question=="CashS",]
mod_ez <- ez::ezANOVA(df, 
                      dv = rating, 
                      wid = ID, 
                      within = .(Image), 
                      type = 1, detailed = TRUE)
print(mod_ez)
```

**Paired t test: Ratings of Support for Cash Assistance**
```{r pairedttest}
# paired t-test of diff btw welfare and non-welfare images on support for cash assistance
df_wide <- df %>%
  spread(Image, rating)
test = t.test(df_wide$NonWelfare, df_wide$Welfare, 
               var.equal = TRUE, 
               paired = TRUE)
test
```

**Graph**
```{r}
ggplot(data = ms, aes(x = Question, y = Mean_Rating, ymin = 1, ymax = 6, colour = Image)) +
  geom_point() +
  geom_errorbar(aes(ymin=Mean_Rating-ci, ymax=Mean_Rating+ci), width=0.2) +
  scale_y_discrete(limits=c(1:6)) +
  coord_flip() +
  scale_colour_manual(values = c("cyan4", "purple4")) +
  theme_classic() +
  ggtitle("Mean Ratings of Critical Images") +
  xlab("Judgment") +
  ylab("Rating") +
  theme(legend.title = element_blank())
```

### Data from original study
```{r}
d.study3 <- read_csv("../data/Study3w1images.csv", na = c("", "NA")) 
d.study3$Question = as.factor(d.study3$Question)
levels(d.study3$Question) <- c("Responsible w Cash Asst","Support of Cash Asst","Responsible w Food Stamps","Support of Food Stamps","Hardworking","Responsible","Smart")

ggplot(data = d.study3, aes(x = Question, y = Mean_Rating, ymin = 1, ymax = 6, colour = Image)) +
  geom_point() +
  geom_errorbar(aes(ymin=Mean_Rating-ci, ymax=Mean_Rating+ci), width=0.2) +
  scale_y_discrete(limits=c(1:6)) +
  coord_flip() +
  scale_colour_manual(values = c("cyan4", "purple4")) +
  theme_classic()  +
  ggtitle("Mean Ratings of Critical Images") +
  xlab("Judgment") +
  ylab("Rating") +
  theme(legend.title = element_blank())
```

### Exploratory analyses

```{r exp_supportubi}
df.btw <- d %>%
  rename(ID = V1) %>%
  select(ID, Secure_UBISupport, Deserve_UBISupport)

test.support = t.test(df.btw$Secure_UBISupport, df.btw$Deserve_UBISupport, 
               var.equal = TRUE, 
               paired = FALSE)
test.support
```

<!-- ## Discussion -->

<!-- ### Summary of Replication Attempt -->

<!-- <!-- Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.   --> -->

<!-- ### Commentary -->

<!-- <!-- Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long. --> -->
